### 2016-10-12 EC17-submitted/intro-old.tex
Copying files not used in submission to EC17-submitted

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admiting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.  Let us explain.

@@

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.  On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.  On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.  Our notions will address both sides of this discussion.
%
%\jnote{We discussed this on the phone, but let me put it in writing here. I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
%
%\tsnote{For me the question is: is security violated once the first FP is found, or the second? My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards. But I do appreciate your point.  A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.  Adapting to what, though? In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.  The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.  The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.  The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.  Each has it's own associated (informal) security interpretation.}
%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle). Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.  Right?}
%
%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}

@@

There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$. This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{schnell2011novel}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

@@

We provide various security notions for these primitives... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenicity of representations, think CDN or P2P settings.}

@@

\heading{Related work: attacks}
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Havent read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}

@@

\tsnote{Perhaps.  I'm still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
%
Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn't the case.  So for the moment, I'll continue to hold my position on this.
%
(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
%
But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
%
I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''. (Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

>>>>

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admitting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchronization. \tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.  Let us explain.

@@

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.  On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter representation of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.  On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.  Our notions will address both sides of this discussion.
%
%\jnote{We discussed this on the phone, but let me put it in writing here. I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
%
%\tsnote{For me the question is: is security violated once the first FP is found, or the second? My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards. But I do appreciate your point.  A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.  Adapting to what, though? In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.  The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.  The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.  The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.  Each has it's own associated (informal) security interpretation.}
%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle). Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.  Right?}
%
%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}

@@

There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$. This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{schnell2011novel}.  (It was subsequently shown not to be secure by Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

@@

We provide various security notions for these primitives... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenticity of representations, think CDN or P2P settings.}

@@

\heading{Related work: attacks}
\begin{itemize}
\item Niedermeyer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Haven't read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}

@@

\tsnote{Perhaps.  I'm still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
%
Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn't the case.  So for the moment, I'll continue to hold my position on this.
%
(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bit-size of the array is smaller than the total bit-size of $S$, yet the combined bit-size of array + hash functions is larger.)
%
But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
%
I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bit-size of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''. (Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

### 2016-10-12 EC17-submitted/lin-correctness.tex
Copying files not used in submission to EC17-submitted

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\TestOracle$ queries will be
false-positives (and, conversely, which will not be), then a
zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\TestOracle$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a zero-query setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

@@

Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives. It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$. Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.

Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries. Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{\setprim}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

>>>>

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\TestOracle$ queries will be
false-positives (and, conversely, which will not be), then a
 FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\TestOracle$, and which require it to return 0;
%return 0.  In this way, no queries ever actually need to be made.
%Moving to a zero-query setting will allow us to connect to classical
%results on the FP-rate of Bloom filters; more in a moment.

@@

Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is an adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives. It must be noted that, by the no-pointless queries assumption and the fact that $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, $\pubaux$ is information theoretically independent of elements not in $S$. Thus, we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.

Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the upperbound on false-positive probability for $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries. Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{\setprim}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]
